---
title: "Week 4 Quizzes"
output: html_document
---

## Practice Quiz

### Question 1: 
Heights of 10 year-olds, regardless of gender, closely follow a normal 
distribution with mean 55 inches and standard deviation 6 inches. Which of the 
following is true?

* __A normal probability plot of heights of a random sample of 500 10 year- olds
people should show a fairly straight line.__
* We would expect more 10 year-olds to be shorter than 55 inches than taller.
* A 10 year-old who is 65 inches tall would be considered more unusual than a 10
year-old who is 45 inches tall.
* Roughly 95% of 10 year-olds are between 37 and 73 inches tall.

### Question 2: 
While it is often assumed that the probabilities of having a boy or a girl are 
the same, the actual probability of having a boy is slightly higher at 0.51. 
Suppose a couple plans to have 3 children. What is the probability that exactly 
2 of them will be boys?

* __.38__ 
* .48
* .58
* .68
* .78

```{r}
dbinom(2, size=3, p=.51)
```

### Question 3: 
You are about to take a multi-day tour through a national park which is famous 
for its wildlife. The tour guide tells you that on any given day there's a 61% 
chance that a visitor will see at least one "big game" animal, and a 39% chance 
they'll see no big game animals; when the tour guide says "big game", he refers 
to either a moose or a bear. The guide assures you that big game sightings on a 
single day are independent of any other day's sightings. Given the information 
from the tour guide, which of the following calculations cannot be performed 
using a binomial distribution?

* Calculate the probability that you see big game on at least 8 days of a 10-day
trip.
* __Calculate the probability that you see at least 4 big game animals on the 
first day of a 5-day trip.__
* Calculate the probability that over a 5-day trip, you see big game on the 
first day and on every day after.
* Calculate the probability that you see big game exactly 0 days of an 8-day 
trip.

### Question 4: 
Your friend is about to begin an introductory chemistry course at his 
university. The course has collected data from students on their study habits 
for many years, and the professor reports that study times (in hours) for the 
final exam closely follow a normal distribution with mean 24 and standard 
deviation 4. What percentage of students study 34 hours or more?

* __Less than 2.5%__
* Between 30% and 35%
* Between 5% and 10%
* Between 15% and 20%
* Between 2.5% and 5%

```{r}
1-pnorm(34, mean=24, sd=4)
```

### Question 5: 
Which of the following is false? Hint: It might be useful to sketch the 
distributions.

* The Z score for the median of a symmetric distribution is approximately 0.
* Calculating percentiles based on the Z table is only appropriate for 
observations that come from (nearly) normal distributions.
* __The Z score for the median of a left skewed distribution is most likely 
negative.__
* Z scores are defined for observations from distributions of any shape and skew.

### Question 6: 
About 30% of human twins are identical, and the rest are fraternal. Identical 
twins are necessarily the same sex, half are males and the other half are 
females. One-quarter of fraternal twins are both male, one-quarter both female, 
and one-half are mixes: one male, one female. You have just become a parent of 
twins and are told they are both girls. Given this information, what is the 
probability that they are identical?

* __46%__
* 72%
* 33%
* 50%

```{r}
p_ident_f <- .3*.5 #P(Identical & F)=P(Identical)*P(F | Identical)
p_frat_f <- .7*.25 #P(Fraternal & F)=P(Fraternall)*P(F | Fraternal)
p_ident_given_f <- p_ident_f / (p_ident_f + p_frat_f)
p_ident_given_f
```

### Question 7: 
Which of the following probabilities can be calculated using the normal 
approximation to the binomial distribution?

* __A clothing store offers store credit cards and only about 17% of the credit 
card holders are males. If we were to randomly sample 100 store credit card 
holders to conduct a survey, what is the probability that at most 20 of the 
sampled individuals would be males?__
* Roughly 20% of Americans smoke. What is the probability that in a random 
sample of 40 people at least 5 are smokers?
* A 2013 Gallup poll reports that 8% of Americans say the situation in Syria is 
the most important issue affecting the U.S. In a randomly selected group of 75 
Americans, what is the probability that more than 10 of them believe the 
situation in Syria is the most important issue facing the U.S.?
* A September 2011 Gallup poll suggests that 56% of Americans do not have a 
great deal of confidence in the mass media to report the news fully, accurately,
and fairly. What is the probability that in a random sample of 20 people, 10 or 
more of them have confidence in the mass media?

## Graded Quiz

### Question 1: 
Suppose IQ scores are normally distributed with mean 100 and standard deviation 
10. Which of the following is false?

* A normal probability plot of IQ scores of a random sample of 1,000 people 
should show a straight line.
* An IQ score greater than 130 is highly unlikely, but not impossible.
* __An IQ score of 80 is more unusual than an IQ score of 120.__
* Roughly 68% of people have IQ scores between 90 and 110.

### Question 2: 
The National Vaccine Information Center estimates that 90% of Americans have had
the disease chickenpox by the time they reach adulthood. What is the probability
that exactly 92 out of 100 randomly sampled American adults had chickenpox 
during childhood?

* .11
* .1
* .07
* .02
* .14

```{r}
dbinom(92, size=100, p=.9)
```

### Question 3: 
Your roommate loves to eat Chinese food for dinner. He estimates that on any 
given night, there's a 30% chance he'll choose to eat Chinese food. Although he 
loves Chinese food, he doesn't like to eat it too much in a short period of 
time, so on most weeks he eats several different kinds of foods for dinner. 
Suppose you wanted to calculate the probability that, over the next 7 days, your
friend eats Chinese food at least 3 times. Which of the following is the most 
accurate statement about calculating this probability?

* Because we know n = 7, k = 3, and p = 0.30, we can use the binomial 
distribution to calculate the desired probability.
* __Because he doesn't like to eat Chinese food too much in a short period of 
time, p is not really the same for each trial and so we cannot use the binomial 
distribution to calculate the desired probability.__
* Because "success" or "failure" have no real meaning in the context of this 
problem, we cannot use the binomial distribution to calculate the desired 
probability.
* Because we do not know the probabilities of your roommate eating any other 
types of foods, we cannot use the binomial distribution to calculate the desired
probability.
* Because we know n = 3, k = 7, and p = 0.30, we can use the binomial 
distribution to calculate the desired probability.

### Question 4: 
Suppose you observe a data point x = 12 and it is known that this data point 
came from a normal distribution with mean 5 and standard deviation 2. Which of 
the following statements is true regarding the observation of x = 12?

* The observation would not be considered unusual, because we know exactly which
normal distribution it comes from.
* The observation would not be considered unusual because it is only about three
standard deviations from the mean.
* The observation would be considered unusual because x = 12 is over twice as 
large as the mean of the distribution.
* The observation would not be considered unusual, because it comes from a 
normal distribution.
* __The observation would be considered unusual because it is farther than three 
standard deviations from the mean.__

### Question 5: 
Which of the following is false? Hint: It might be useful to sketch the 
distributions.

* If observations don't come from a distribution that's nearly normal, we can't 
calculate percentiles based on the Z table.
* __If you calculated the Z score for the median of a right skewed distribution, 
you'd most likely get a positive number.__
* Regardless of the shape and skew of a distribution, Z scores are still defined
and can be calculated for observations from that distribution.
* The Z score for the median of a symmetric distribution is approximately 0.

### Question 6: 
More than three-quarters of the nation's colleges and universities now offer 
online classes, and about 23% of college graduates have taken a course online. 
39% of those who have taken a course online believe that online courses provide 
the same educational value as one taken in person, a view shared by only 27% of 
those who have not taken an online course. At a coffee shop you overhear a 
recent college graduate discussing that she doesn't believe that online courses 
provide the same educational value as one taken in person. What's the 
probability that she has taken an online course before?

* .2079
* .3014
* __.1997__
* .1403

```{r}
p_online <- .23
p_val_g_online <- .39
p_val_g_notonline <- .27
p_notval_online <- p_online * (1-p_val_g_online)
p_notval_notonline <- (1-p_online) * (1-p_val_g_notonline)
p_online_g_notval <- p_notval_online / (p_notval_online + p_notval_notonline)
p_online_g_notval
```

### Question 7: 
Your boss is a biologist who needs wood samples from long-leaf pine trees with a
fungal disease which is only visible under a microscope, and she sends you on an
assignment to collect the samples. She wants at least 50 different diseased 
samples. She tells you that approximately 28% of long-leaf pine trees currently 
have the fungal disease. If you sample 160 long-leaf pine trees at random, what 
is the probability you'll have at least 50 diseased samples to return to your 
boss? (Use the normal approximation to calculate this probability.)

* 82%
* 18%
* 13%
* 92%
* 28%

```{r}
# normal approximation
p_disease <- .28
sample <- 160
mean <- p_disease * sample
sd <- sqrt(p_disease * sample * (1-p_disease))
1-pnorm(49.5, mean=mean, sd=sd)

#exact calculation
sum(dbinom(50:160, size=160, p=.28))
```